A multi-dimensional extension of the Lightweight Temporal Compression method

### 2018-10-17 paper.tex
fix yrange of figures and fix epsilon

\paragraph{Inifinity vs Euclidean norms}
Compared to the infinity norm, the average ratio between the compression ratios obtained
with the infinity and Euclidean norm is 1.08 for 2D data, and 1.20 
for 3D data. These ratios are lower than the theoretical values of 
$\frac{4}{\pi}$ in 2D and $\frac{6}{\pi}$ in 3D, which are obtained for 
random-uniform signals. Unsurprisingly, the infinity norm surpasses the 
Euclidean norm in terms of resource consumption. Memory-wise, the 
infinity norm requires a constant amount of 80~B, used to store the 
intersection of n-balls. The Euclidean norm, however, uses up to 4.9~KB of memory 
for the Long time series in 3D with $\epsilon=100$. More importantly, 
the amount of required memory increases for more complex time series 
(Long vs Short), and it also increases with larger 
values of $\epsilon$. Similar observations are made for the processing 
time, with values ranging from 0.2~ms for the simplest time series and 
smallest $\epsilon$, to 26.4~ms for the most complex time series and 
largest $\epsilon$.

\paragraph{2D vs 3D}
For a given $\epsilon$ of 100 and a given time series, the compression 
ratios are always higher in 2D than in 3D. It makes sense since the 
probability for the signal to deviate from a straight line 
approximation is higher in 3D than it is in 2D. Besides, resource 
consumption is higher in 3D than in 2D: for the infinity norm, 3D 
consumes 1.4 times more memory than 2D (1.6 times on average for 
Euclidean norm), and processing time is 1.3 longer on average (1.18 on 
average for Euclidean norm).

>>>>

\paragraph{Inifinity vs Euclidean norms}
Compared to the infinity norm, the average ratio between the compression ratios obtained
with the infinity and Euclidean norm is 1.08 for 2D data, and 1.20
for 3D data. These ratios are lower than the theoretical values of
$\frac{4}{\pi}$ in 2D and $\frac{6}{\pi}$ in 3D, which are obtained for
random-uniform signals. Unsurprisingly, the infinity norm surpasses the
Euclidean norm in terms of resource consumption. Memory-wise, the
infinity norm requires a constant amount of 80~B, used to store the
intersection of n-balls. The Euclidean norm, however, uses up to 4.9~KB of memory
for the Long time series in 3D with $\epsilon=48.8~mg$. More importantly,
the amount of required memory increases for more complex time series
(Long vs Short), and it also increases with larger
values of $\epsilon$. Similar observations are made for the processing
time, with values ranging from 0.2~ms for the simplest time series and
smallest $\epsilon$, to 26.4~ms for the most complex time series and
largest $\epsilon$.

\paragraph{2D vs 3D}
For a given $\epsilon$ of 48.8~mg and a given time series, the compression 
ratios are always higher in 2D than in 3D. It makes sense since the
probability for the signal to deviate from a straight line
approximation is higher in 3D than it is in 2D. Besides, resource
consumption is higher in 3D than in 2D: for the infinity norm, 3D
consumes 1.4 times more memory than 2D (1.6 times on average for
Euclidean norm), and processing time is 1.3 longer on average (1.18 on
average for Euclidean norm).
